### 2021-03-31 README.Rmd
new code of conduct on README
Installation instructions following pkg targets

At this stage `dataaimsr` is not hosted on CRAN R package network, although
we re aiming to submit it there very soon. For the moment, an alternative
method of installation is to use the R `remotes` package. R `remotes` can be
installed using the following command:

```{r, eval = FALSE}
install.packages("remotes")
```

After `remotes` has been installed `dataaimsr` can be installed directly from
GitHub using the following command:

```{r, eval = FALSE}
remotes::install_github("https://github.com/ropensci/dataaimsr")
```

This command will also install the three package dependencies: `httr`,
`jsonlite` and `parsedate`.

@@

>>>>

Type | Source | Command
---|---|---
Release | CRAN | Not yet available
Development | GitHub | `remotes::install_github("ropensci/dataaimsr")`
Development | rOpenSci | `install.packages("dataaimsr", repos = "https://dev.ropensci.org")`

@@

## Code of Conduct

Please note that this package is released with a
[Contributor Code of Conduct](https://ropensci.org/code-of-conduct/).
By contributing to this project, you agree to abide by its terms.
